\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1.25cm]{geometry}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[
  colorlinks=true,
  urlcolor=linkred,
  linkcolor=linkred,
  citecolor=linkred
]{hyperref}

\definecolor{linkred}{HTML}{8F2D1C}
\definecolor{sectionslate}{HTML}{4F6673}
\definecolor{textdark}{HTML}{201B17}
\definecolor{mutedtext}{HTML}{5D6970}

\setlength{\parindent}{0pt}
\setlist[itemize]{nosep,leftmargin=1.25em,topsep=0.15em,itemsep=0.05em}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\normalsize\bfseries\color{sectionslate}}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{0.08em}{\color{sectionslate}\titlerule}]
\titlespacing*{\section}{0pt}{0.85em}{0.45em}

\newcommand{\resumeheader}[4]{
  {\huge\textbf{\textcolor{textdark}{#1}}}\par
  \textcolor{mutedtext}{#2 \textbar\ #3 \textbar\ \href{mailto:#4}{#4}}\par
  \textcolor{mutedtext}{\href{https://github.com/Chr1sC0de/}{github.com/Chr1sC0de}
  \textbar\
  \href{https://chr1sc0de.github.io/Resume/}{chr1sc0de.github.io/Resume}}\par
}

\newcommand{\resumesection}[1]{\section*{#1}}

\newenvironment{resumejob}[3]{
  \par\addvspace{0.45em}
  \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{0.3\textwidth}@{}}
    \textbf{\textcolor{textdark}{#1}} & \textcolor{mutedtext}{#2} \\
    \multicolumn{2}{@{}l@{}}{\textit{\textcolor{mutedtext}{#3}}}
  \end{tabularx}
  \vspace{-0.55em}
}{
  \par\addvspace{0.2em}
}

\newcommand{\resumeproject}[2]{
  \par\addvspace{0.2em}
  \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{0.36\textwidth}@{}}
    \textbf{\textcolor{textdark}{#1}} & #2
  \end{tabularx}
  \vspace{-0.55em}
}

\begin{document}

\resumeheader{Chris Mamon}{Melbourne, Australia}{+61 413 016 929}{chrisam1993@live.com}

\resumesection{Profile}
Data scientist and backend-focused Python developer with experience building and operating production data platforms, ETL systems, CI/CD pipelines, and forecasting workflows. Strong background in platform reliability, deployment automation, and code quality, with research roots in computational fluid dynamics and extensive scientific programming experience.

\resumesection{Projects}
\resumeproject{Energy Market Delta Lake (Proof of Concept)}{\href{https://github.com/Chr1sC0de/energy-market-delta-lake}{GitHub} \textbar\ \href{https://ausenergymarketdata.com/dagster-webserver/guest}{Dagster Guest Demo}}
\begin{itemize}
  \item Built a Python, AWS, and Dagster proof of concept for ingesting, orchestrating, cleansing, and serving Australian energy market data through an event-driven ETL and lakehouse architecture.
  \item Designed and deployed 200+ assets across S3-backed Delta tables, PostgreSQL metadata, DynamoDB locking, ECS services, and Pulumi-managed infrastructure as code.
  \item Applied code quality automation, testing, and Codex AI-assisted implementation across ETL patterns, deployment setup, and platform documentation.
\end{itemize}

\resumesection{Employment}

\begin{resumejob}{Data Scientist, AEMO}{Nov 2025 -- Current}{Melbourne}
Teams: NEM Operational Forecasting
\begin{itemize}
  \item Refactored and enhanced a Python-based Dagster ETL on Windows supporting around 50 assets for NEM operations, improving reliability across high-frequency backend workloads.
  \item Maintained R script ETL, Python scripts, and Podman-containerized jobs, with Dagster coordinating mixed execution patterns across operational forecasting workflows.
  \item Reduced failure rates in minute-level batch jobs by fixing networking and implementation issues, and migrated Dagster metadata from SQLite to Postgres to reduce cross-run impact.
  \item Standardized backend implementation patterns through factory-based refactors, improving consistency and making new asset and pipeline development easier to extend.
  \item Strengthened Azure DevOps CI/CD with Bash automation, Ruff, Prek, Pytest, and Mypy, improving code quality and deployment reliability.
  \item Built Pyinfra-based Dagster deployment, distributed Podman deployment, and multi-repository gRPC deployment, moving delivery from Windows Server toward self-hosted Linux CI/CD.
  \item Performed quarterly retraining and production deployment of Frequency Uncertainty Models, and fed BOM ensemble model data into ML forecasting pipelines.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Gas Market Analyst, AEMO}{Nov 2024 -- Oct 2025}{Melbourne}
Teams: Gas Market Real-Time Operations
\begin{itemize}
  \item \textbf{Reporting}: Maintained a VBA reporting tool for weekly market insights and rotated analysis delivery.
  \item \textbf{Process Automation}
  \begin{itemize}
    \item Automated extraction and validation of monthly AER and AEMO public data uploads using Python, saving about two hours per report.
    \item Streamlined gas dataset QA with Python and Marimo notebooks, accelerating Quarterly Energy Dynamics validation.
  \end{itemize}
  \item \textbf{Operations Dashboards}
  \begin{itemize}
    \item Built dashboards for contingency gas operations, expiring trading rights, MOS stack checks, STTM and DWGM bids and offers, company contacts, and legacy NEOMobile report reconstruction.
  \end{itemize}
  \item \textbf{Operating System Lifecycle Testing}
  \begin{itemize}
    \item Tested application server upgrades from Microsoft SQL Server 2017 to 2022.
    \item Automated stored procedure validation with Pytest to ensure UAT outputs matched production results.
    \item Coordinated integration testing with cross-functional teams.
  \end{itemize}
\end{itemize}
\end{resumejob}

\begin{resumejob}{Data \& Performance Analyst, Origin Energy}{Nov 2023 -- Nov 2024}{Melbourne}
Teams: LPG Data Systems \& Performance
\begin{itemize}
  \item \textbf{Documentation and Collaboration}: Documented requirements in Confluence, collaborated through Asana, and worked in a GitOps-enabled Agile dashboard team.
  \item \textbf{Stock Reconciliation}
  \begin{itemize}
    \item Automated Salesforce, SAP, and IVMS integration into Redshift with scheduled Matillion jobs.
    \item Built a local Dagster-style pipeline connecting RoutePlanner, SharePoint, SGFleet, IVMS, SAP, Salesforce, and Outlook during an integration uplift.
    \item Led requirements, data-model identification, ETL oversight, and dashboard delivery for LPG stock reconciliation.
  \end{itemize}
  \item \textbf{Asset Performance}
  \begin{itemize}
    \item Built end-to-end analytics dashboards using Salesforce and IVMS data to optimize truck scheduling and asset use, contributing to about \$500,000 in cost savings.
    \item Created reports that audited driver telemetry entries and exposed data-capture reliability issues for continuous improvement.
  \end{itemize}
\end{itemize}
\end{resumejob}

\begin{resumejob}{Market Analyst \& Analytics Developer, Energy Australia}{Jun 2022 -- Nov 2023}{Melbourne}
Teams: Trading Persistent and Trading Data \& Systems
\begin{itemize}
  \item \textbf{Documentation and Collaboration}: Documented business and technical requirements in Confluence and collaborated through Jira using Agile delivery practices.
  \item \textbf{Plexos Data Extract}
  \begin{itemize}
    \item Developed a PySpark cloud ETL pipeline to extract Plexos forecasts into Databricks Delta tables.
    \item Reduced trader analysis time by more than eight hours through pipeline optimization.
    \item Orchestrated on-prem to cloud integration with Apache Airflow and Databricks ingestion tasks.
    \item Added S3-triggered ingestion, New Relic logging and alerts, Terraform and Azure Pipelines automation, Python library deployment, and automated test, coverage, and SonarQube reporting.
  \end{itemize}
  \item \textbf{Hedging Strategy}
  \begin{itemize}
    \item Implemented hedging position logic in Databricks and built scheduled Airflow DAGs that coordinated workflows across accounts.
    \item Automated Databricks Photon activation in Azure DevOps deployment pipelines.
  \end{itemize}
  \item \textbf{Cloud Data Program}: Repeatedly executed automated business verification testing during a mission-critical lift-and-shift migration to preserve data accuracy and business continuity.
  \item \textbf{AEMO Market Compensation Analysis}: Calculated compensation required from market price caps and identified an amount of about \$3 million.
  \item \textbf{Caps Book Performance Evaluation}: Supported dashboard query design comparing manual trades against automated strategy performance.
  \item \textbf{CorvU Migration Support}: Wrote SQL queries that helped migrate reports from external software into internal databases and Tableau services.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Research Assistant, The University of Melbourne}{Jan 2018 -- Jan 2021}{Melbourne}
Teams: Blood Flow and Deep Learning
\begin{itemize}
  \item Developed and documented scientific C++ and Python code for numerical modeling, visualization, and statistical analysis used in publications.
  \item Implemented computational fluid dynamics simulations on high-performance computing systems.
  \item Trialed convolutional neural networks for OCT image segmentation and shear stress prediction.
  \item Co-authored peer-reviewed journal papers listed under Publications.
\end{itemize}
\end{resumejob}

\resumesection{Education}
\textbf{Masters of Engineering (With Distinction), Mechanical Specialization, The University of Melbourne}\hfill Jan 2015 -- Jul 2017\par
Melbourne \textbar\ \href{https://www.myequals.net/r/sharelink/39bf60f2-2f95-49f6-9c2f-03867a939c90/4a5a7492-b23c-4e9e-87b3-d58a3a20dd87}{Academic Transcript}\par
\vspace{0.3em}
\textbf{Bachelor of Science, The University of Melbourne}\hfill Jan 2012 -- Dec 2014\par
Melbourne

\resumesection{Courses and Certificates}
\begin{itemize}
  \item \href{https://coursera.org/share/e7c8acd9ef97ec13153d23b97eb3ae3d}{Data Engineering, IBM on Coursera}
  \item \href{https://coursera.org/share/a9b1cae25a73e890d4bf699594b8171b}{PostgreSQL for Everybody, University of Michigan on Coursera}
  \item \href{https://coursera.org/share/5eeef59e6fec2ea34ab6729866b8c30a}{AWS Cloud Technical Essentials, AWS on Coursera}
  \item \href{https://www.coursera.org/account/accomplishments/specialization/certificate/XCXYLXJZ4CHS}{Applied Data Science with Python, University of Michigan on Coursera}
  \item \href{https://www.coursera.org/account/accomplishments/specialization/certificate/BK4XG9PK8ESF}{Data Analytics, Google on Coursera}
  \item \href{https://www.coursera.org/account/accomplishments/specialization/certificate/ZDETFK6UQFGF}{Excel Skills for Data Analytics and Visualization, Macquarie University on Coursera}
\end{itemize}

\resumesection{Publications}
\href{https://1drv.ms/u/s!AqKmu53lUHwmiphhitj54APJmTTs7A?e=oJdxgG}{Link to Articles}
\begin{itemize}
  \item ``Computational fluid dynamics comparisons of wall shear stress in patient-specific coronary artery bifurcation using coronary angiography and optical coherence tomography'', APS Division of Fluid Dynamics, August 2016
  \item ``Effect of Medical Imaging Modalities on the simulated blood flow through a 3D reconstructed stented coronary artery segment'', 20th Australasian Fluid Mechanics Conference Perth, December 2016
  \item ``Some new characteristics of the confined flow over circular cylinders at low Reynolds numbers'', International Journal of Heat and Fluid Flow, December 2020
  \item ``High Spatial Endothelial Shear Stress Gradient Independently Predicts Site of Acute Coronary Plaque Rupture and Erosion'', Journal of Cardiovascular Research, July 2021
  \item ``High Endothelial Shear Stress and Stress Gradient at Plaque Erosion Persist up to 12 Months'', International Journal of Cardiology, June 2022
\end{itemize}

\resumesection{Skills}
\begin{tabularx}{\textwidth}{@{}XXXX@{}}
Apache Airflow & AWS and Databricks & Azure DevOps & C++ \\
Codex & Dagster & Data Analysis and Cleansing & DAX \\
Excel VBA & M & MATLAB & Microsoft Power BI \\
Microsoft Power Query & OpenFOAM & Paraview & Podman \\
Powershell & Pyinfra & Python & R \\
Postgres, Oracle, MSSQL & SolidWorks & Tableau & Terraform \\
\end{tabularx}

\end{document}
