\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1.25cm]{geometry}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[
  colorlinks=true,
  urlcolor=linkred,
  linkcolor=linkred,
  citecolor=linkred
]{hyperref}

\definecolor{linkred}{HTML}{8F2D1C}
\definecolor{sectionslate}{HTML}{4F6673}
\definecolor{textdark}{HTML}{201B17}
\definecolor{mutedtext}{HTML}{5D6970}

\setlength{\parindent}{0pt}
\setlist[itemize]{nosep,leftmargin=1.25em,topsep=0.15em,itemsep=0.05em}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\normalsize\bfseries\color{sectionslate}}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{0.08em}{\color{sectionslate}\titlerule}]
\titlespacing*{\section}{0pt}{0.85em}{0.45em}

\newcommand{\resumeheader}[4]{
  {\huge\textbf{\textcolor{textdark}{#1}}}\par
  \textcolor{mutedtext}{#2 \textbar\ #3 \textbar\ \href{mailto:#4}{#4}}\par
  \textcolor{mutedtext}{\href{https://github.com/Chr1sC0de/}{github.com/Chr1sC0de}
  \textbar\
  \href{https://chr1sc0de.github.io/Resume/}{chr1sc0de.github.io/Resume}
  \textbar\
  \href{platform-resume.pdf}{One-page ML platform resume}}\par
}

\newcommand{\resumesection}[1]{\section*{#1}}

\newenvironment{resumejob}[3]{
  \par\addvspace{0.45em}
  \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{0.3\textwidth}@{}}
    \textbf{\textcolor{textdark}{#1}} & \textcolor{mutedtext}{#2} \\
    \multicolumn{2}{@{}l@{}}{\textit{\textcolor{mutedtext}{#3}}}
  \end{tabularx}
  \vspace{-0.55em}
}{
  \par\addvspace{0.2em}
}

\newcommand{\resumeproject}[2]{
  \par\addvspace{0.2em}
  \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{0.36\textwidth}@{}}
    \textbf{\textcolor{textdark}{#1}} & #2
  \end{tabularx}
  \vspace{-0.55em}
}

\begin{document}

\resumeheader{Chris Mamon}{Melbourne, Australia}{+61 413 016 929}{chrisam1993@live.com}

\resumesection{Profile}
ML platform-oriented Python engineer and data scientist with experience building Dagster, AWS, and containerized data platforms for operational forecasting, lakehouse pipelines, and model delivery. Strong background in CI/CD, infrastructure as code, orchestration reliability, Postgres-backed metadata stores, local cloud emulation, and scientific computing.

\resumesection{Selected Platform Project}
\resumeproject{Energy Market Delta Lake (AWS/Dagster Platform Proof of Concept)}{\href{https://github.com/Chr1sC0de/energy-market-delta-lake}{GitHub} \textbar\ \href{https://ausenergymarketdata.com/dagster-webserver/guest}{Dagster Guest Demo}}
\begin{itemize}
  \item Built and deployed a Python, AWS, and Dagster lakehouse proof of concept for Australian energy market data, covering ingestion, orchestration, validation, storage, and public exploration.
  \item Provisioned the platform with Pulumi across VPC networking, IAM, ECR, ECS Fargate/Fargate Spot services, S3 buckets, DynamoDB Delta locking, PostgreSQL metadata storage, Caddy, authentication, and Marimo dashboards.
  \item Implemented 200+ Dagster assets and checks across scheduled discovery, event-driven ingestion, bronze Delta tables, source-specific silver snapshots, shared gas-model facts and dimensions, sensors, schedules, and Delta maintenance.
  \item Built local and promotion-style validation with Podman, LocalStack, Postgres, cached archive seeds, Dagster GraphQL launches, dependency-wave asset batches, asset-check monitoring, and regression budgets.
  \item Documented operator workflows, ADRs, test lanes, code-location manifests, dashboard behavior, and agent-assisted delivery loops so the platform can be reviewed and extended from the repository.
\end{itemize}

\resumesection{Employment}

\begin{resumejob}{Data Scientist, AEMO}{Nov 2025 -- Present}{Melbourne}
Teams: NEM Operational Forecasting
\begin{itemize}
  \item Refactored and operated a Python-based Dagster ETL on Windows supporting around 50 assets for NEM operations, improving reliability across high-frequency operational forecasting workloads.
  \item Stabilized minute-level batch jobs by fixing networking and implementation issues, and migrated Dagster metadata from SQLite to Postgres to reduce cross-run impact.
  \item Built Pyinfra-based Dagster deployment, distributed Podman deployment, and multi-repository gRPC deployment patterns, moving delivery from Windows Server toward self-hosted Linux CI/CD.
  \item Maintained R script ETL, Python scripts, and Podman-containerized jobs, with Dagster coordinating mixed execution patterns across forecasting workflows.
  \item Standardized backend implementation patterns through factory-based refactors, improving consistency and making new assets and pipelines easier to extend.
  \item Strengthened Azure DevOps CI/CD with Bash automation, Ruff, Prek, Pytest, and Mypy, improving code quality and deployment reliability.
  \item Performed quarterly retraining and production deployment of Frequency Uncertainty Models, and fed BOM ensemble model data into ML forecasting pipelines.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Gas Market Analyst, AEMO}{Nov 2024 -- Oct 2025}{Melbourne}
Teams: Gas Market Real-Time Operations
\begin{itemize}
  \item Maintained VBA reporting for weekly gas market insights and rotated analysis delivery.
  \item Automated extraction and validation of monthly AER and AEMO public data uploads using Python, saving about two hours per report.
  \item Streamlined gas dataset QA with Python and Marimo notebooks, accelerating Quarterly Energy Dynamics validation.
  \item Built dashboards for contingency gas operations, expiring trading rights, MOS stack checks, STTM and DWGM bids and offers, company contacts, and legacy NEOMobile report reconstruction.
  \item Tested application server upgrades from Microsoft SQL Server 2017 to 2022, automated stored procedure validation with Pytest, and coordinated UAT with cross-functional teams.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Data \& Performance Analyst, Origin Energy}{Nov 2023 -- Nov 2024}{Melbourne}
Teams: LPG Data Systems \& Performance
\begin{itemize}
  \item Documented requirements in Confluence, collaborated through Asana, and worked in a GitOps-enabled Agile dashboard team.
  \item Automated Salesforce, SAP, and IVMS integration into Redshift with scheduled Matillion jobs.
  \item Built a local Dagster-style pipeline connecting RoutePlanner, SharePoint, SGFleet, IVMS, SAP, Salesforce, and Outlook during an integration uplift.
  \item Led requirements, data-model identification, ETL oversight, and dashboard delivery for LPG stock reconciliation.
  \item Built end-to-end analytics dashboards using Salesforce and IVMS data to optimize truck scheduling and asset use, contributing to about \$500,000 in cost savings.
  \item Created reports that audited driver telemetry entries and exposed data-capture reliability issues for continuous improvement.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Market Analyst \& Analytics Developer, Energy Australia}{Jun 2022 -- Nov 2023}{Melbourne}
Teams: Trading Persistent and Trading Data \& Systems
\begin{itemize}
  \item Documented business and technical requirements in Confluence and collaborated through Jira using Agile delivery practices.
  \item Developed a PySpark cloud ETL pipeline to extract Plexos forecasts into Databricks Delta tables, reducing trader analysis time by more than eight hours.
  \item Orchestrated on-prem to cloud integration with Apache Airflow and Databricks ingestion tasks.
  \item Added S3-triggered ingestion, New Relic logging and alerts, Terraform and Azure Pipelines automation, Python library deployment, and automated test, coverage, and SonarQube reporting.
  \item Implemented hedging position logic in Databricks and built scheduled Airflow DAGs that coordinated workflows across accounts.
  \item Automated Databricks Photon activation in Azure DevOps deployment pipelines.
  \item Repeatedly executed automated business verification testing during a mission-critical lift-and-shift migration to preserve data accuracy and business continuity.
  \item Calculated AEMO market compensation required from market price caps and identified an amount of about \$3 million.
  \item Supported dashboard query design comparing manual trades against automated strategy performance.
  \item Wrote SQL queries that helped migrate reports from external software into internal databases and Tableau services.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Research Assistant, The University of Melbourne}{Jan 2018 -- Jan 2021}{Melbourne}
Teams: Blood Flow and Deep Learning
\begin{itemize}
  \item Developed and documented scientific C++ and Python code for numerical modeling, visualization, and statistical analysis used in publications.
  \item Implemented computational fluid dynamics simulations on high-performance computing systems.
  \item Trialed convolutional neural networks for OCT image segmentation and shear stress prediction.
  \item Co-authored peer-reviewed journal papers listed under Publications.
\end{itemize}
\end{resumejob}

\resumesection{Education}
\textbf{Masters of Engineering (With Distinction), Mechanical Specialization, The University of Melbourne}\hfill Jan 2015 -- Jul 2017\par
Melbourne \textbar\ \href{https://www.myequals.net/r/sharelink/39bf60f2-2f95-49f6-9c2f-03867a939c90/4a5a7492-b23c-4e9e-87b3-d58a3a20dd87}{Academic Transcript}\par
\vspace{0.3em}
\textbf{Bachelor of Science, The University of Melbourne}\hfill Jan 2012 -- Dec 2014\par
Melbourne

\resumesection{Courses and Certificates}
\begin{itemize}
  \item \href{https://coursera.org/share/e7c8acd9ef97ec13153d23b97eb3ae3d}{Data Engineering, IBM on Coursera}
  \item \href{https://coursera.org/share/a9b1cae25a73e890d4bf699594b8171b}{PostgreSQL for Everybody, University of Michigan on Coursera}
  \item \href{https://coursera.org/share/5eeef59e6fec2ea34ab6729866b8c30a}{AWS Cloud Technical Essentials, AWS on Coursera}
  \item \href{https://www.coursera.org/account/accomplishments/specialization/certificate/XCXYLXJZ4CHS}{Applied Data Science with Python, University of Michigan on Coursera}
  \item \href{https://www.coursera.org/account/accomplishments/specialization/certificate/BK4XG9PK8ESF}{Data Analytics, Google on Coursera}
  \item \href{https://www.coursera.org/account/accomplishments/specialization/certificate/ZDETFK6UQFGF}{Excel Skills for Data Analytics and Visualization, Macquarie University on Coursera}
\end{itemize}

\resumesection{Publications}
\href{https://1drv.ms/u/s!AqKmu53lUHwmiphhitj54APJmTTs7A?e=oJdxgG}{Link to Articles}
\begin{itemize}
  \item ``Computational fluid dynamics comparisons of wall shear stress in patient-specific coronary artery bifurcation using coronary angiography and optical coherence tomography'', APS Division of Fluid Dynamics, August 2016
  \item ``Effect of Medical Imaging Modalities on the simulated blood flow through a 3D reconstructed stented coronary artery segment'', 20th Australasian Fluid Mechanics Conference Perth, December 2016
  \item ``Some new characteristics of the confined flow over circular cylinders at low Reynolds numbers'', International Journal of Heat and Fluid Flow, December 2020
  \item ``High Spatial Endothelial Shear Stress Gradient Independently Predicts Site of Acute Coronary Plaque Rupture and Erosion'', Journal of Cardiovascular Research, July 2021
  \item ``High Endothelial Shear Stress and Stress Gradient at Plaque Erosion Persist up to 12 Months'', International Journal of Cardiology, June 2022
\end{itemize}

\resumesection{Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries\color{textdark}}lX@{}}
Platform and cloud & AWS, Pulumi, Terraform, ECS/Fargate, ECR, IAM, VPC, S3, DynamoDB, Postgres, LocalStack \\
Data and MLOps & Dagster, Apache Airflow, Databricks, Delta Lake, PySpark, Polars, Pandas, model retraining and deployment \\
DevEx and quality & Python, uv, Pytest, Ruff, Prek, Mypy, Zuban, Bash, Azure DevOps, CI/CD, GitHub, Codex \\
Containers and deployment & Podman, Docker-compatible workflows, Linux services, Pyinfra, Caddy, FastAPI \\
Analytics and domain & SQL, R, Power BI, Tableau, energy market operations, operational forecasting data \\
Scientific computing & C++, MATLAB, OpenFOAM, Paraview, computational fluid dynamics, high-performance computing \\
\end{tabularx}

\end{document}
