\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1.02cm]{geometry}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[
  colorlinks=true,
  urlcolor=linkred,
  linkcolor=linkred,
  citecolor=linkred
]{hyperref}

\definecolor{linkred}{HTML}{8F2D1C}
\definecolor{sectionslate}{HTML}{4F6673}
\definecolor{textdark}{HTML}{201B17}
\definecolor{mutedtext}{HTML}{5D6970}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.18em}
\setlist[itemize]{nosep,leftmargin=1.15em,topsep=0.08em,itemsep=0.02em}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\small\bfseries\color{sectionslate}}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{0.05em}{\color{sectionslate}\titlerule}]
\titlespacing*{\section}{0pt}{0.48em}{0.25em}

\newcommand{\resumeheader}[4]{
  {\LARGE\textbf{\textcolor{textdark}{#1}}}\par
  \textcolor{mutedtext}{#2 \textbar\ #3 \textbar\ \href{mailto:#4}{#4}}\par
  \textcolor{mutedtext}{\href{https://github.com/Chr1sC0de/}{github.com/Chr1sC0de}
  \textbar\
  \href{https://chr1sc0de.github.io/Resume/}{Technical CV}
  \textbar\
  \href{https://github.com/Chr1sC0de/energy-market-delta-lake}{Energy Market Delta Lake}}\par
}

\newcommand{\resumesection}[1]{\section*{#1}}

\newenvironment{resumejob}[3]{
  \par\addvspace{0.28em}
  \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{0.28\textwidth}@{}}
    \textbf{\textcolor{textdark}{#1}} & \textcolor{mutedtext}{#2} \\
    \multicolumn{2}{@{}l@{}}{\textit{\textcolor{mutedtext}{#3}}}
  \end{tabularx}
  \vspace{-0.62em}
}{
  \par\addvspace{0.06em}
}

\newcommand{\resumeproject}[2]{
  \par\addvspace{0.12em}
  \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{0.34\textwidth}@{}}
    \textbf{\textcolor{textdark}{#1}} & #2
  \end{tabularx}
  \vspace{-0.62em}
}

\begin{document}
\fontsize{9.25}{10.15}\selectfont

\resumeheader{Chris Mamon}{ML Platform Engineer \textbar\ Melbourne, Australia}{+61 413 016 929}{chrisam1993@live.com}

\resumesection{Profile}
Python platform engineer focused on ML and data-platform reliability, with experience building Dagster, AWS, and containerized systems for operational forecasting, model retraining, lakehouse pipelines, CI/CD, and developer workflows.

\resumesection{Selected Platform Project}
\resumeproject{Energy Market Delta Lake (AWS/Dagster Proof of Concept)}{\href{https://ausenergymarketdata.com/dagster-webserver/guest}{Demo} \textbar\ \href{https://github.com/Chr1sC0de/energy-market-delta-lake}{GitHub}}
\begin{itemize}
  \item Built a public AWS/Dagster lakehouse for Australian energy data using Pulumi, VPC/IAM/ECR/ECS, S3 Delta/Parquet storage, DynamoDB Delta locking, Postgres metadata, Caddy/auth, and Marimo dashboards.
  \item Implemented 200+ assets and checks across scheduled discovery, event-driven ingestion, bronze Delta tables, source-specific silver snapshots, gas-model marts, sensors, schedules, and maintenance jobs.
  \item Added Podman/LocalStack local parity, cached archive seeds, Dagster GraphQL e2e launches, dependency-wave asset batches, asset-check monitoring, and regression budgets.
\end{itemize}

\resumesection{Platform Experience}
\begin{resumejob}{Data Scientist, AEMO}{Nov 2025 -- Present}{NEM Operational Forecasting}
\begin{itemize}
  \item Refactored and operated a Python/Dagster ETL with around 50 assets for high-frequency operational forecasting workloads.
  \item Stabilized minute-level batch jobs by fixing networking/runtime issues and migrating Dagster metadata from SQLite to Postgres.
  \item Built Pyinfra, Podman, and multi-repository gRPC deployment patterns to move delivery toward self-hosted Linux CI/CD.
  \item Strengthened Azure DevOps quality gates with Bash, Ruff, Prek, Pytest, Mypy, and reusable asset factory patterns.
  \item Retrained and deployed Frequency Uncertainty Models; fed BOM ensemble data into ML forecasting pipelines.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Market Analyst \& Analytics Developer, Energy Australia}{Jun 2022 -- Nov 2023}{Trading Data \& Systems}
\begin{itemize}
  \item Built a PySpark, Airflow, and Databricks Delta ingestion pipeline for Plexos forecasts, reducing trader analysis time by more than eight hours.
  \item Added S3-triggered ingestion, New Relic logging and alerts, Terraform, Azure Pipelines, Python package deployment, automated tests, coverage, and SonarQube reporting.
  \item Implemented hedging position logic in Databricks and scheduled Airflow DAGs across accounts.
\end{itemize}
\end{resumejob}

\begin{resumejob}{Earlier Platform and Analytics Roles}{2018 -- 2025}{AEMO Gas, Origin Energy, University of Melbourne}
\begin{itemize}
  \item Automated AEMO/AER data validation, SQL Server upgrade checks, Redshift integrations, and Marimo QA notebooks; used Pytest to compare UAT and production stored procedure outputs.
  \item Delivered Salesforce, SAP, IVMS, and telemetry analytics that supported LPG stock reconciliation and about \$500,000 in asset-use savings.
  \item Developed C++/Python scientific computing code on HPC systems and trialed CNNs for OCT image segmentation and shear stress prediction.
\end{itemize}
\end{resumejob}

\resumesection{Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries\color{textdark}}lX@{}}
Platform/cloud & AWS, Pulumi, Terraform, ECS/Fargate, ECR, IAM, VPC, S3, DynamoDB, Postgres, LocalStack \\
MLOps/data & Dagster, Airflow, Databricks, Delta Lake, PySpark, Polars, Pandas, model retraining and deployment \\
DevEx/quality & Python, uv, Pytest, Ruff, Prek, Mypy, Zuban, Bash, Azure DevOps, CI/CD, GitHub, Codex \\
Containers & Podman, Docker-compatible workflows, Linux services, Pyinfra, Caddy, FastAPI \\
\end{tabularx}

\resumesection{Education}
\textbf{Masters of Engineering (With Distinction), The University of Melbourne}\hfill 2015 -- 2017\par
\textbf{Bachelor of Science, The University of Melbourne}\hfill 2012 -- 2014

\end{document}
